A User-Extensible and Adaptable Parser Architecture

### 2008-08-20 doc/sgai-2008.tex
Spelling checked. Checked URLs in bibliography. Run chktex on the bibliographies. Made ATN an acronym.

\newacronym{PDA}{Pushdown Automata}{}
\newacronym{FA}{Finite Automata}{}
\newacronym{CFL}{Context-Free Languages}{}
\newacronym{SLCT}{Simple Logfile Clustering Tool}{}
\newacronym{SMTP}{Simple Mail Transfer Protocol}{}

@@

There is some similarity (shown in \tableref{Similarities with ATN})
between the architecture and William Wood's Augmented Transition Networks
(ATN)~\cite{atns, nlpip}, a tool used in Computational Linguistics for
creating grammars to parse or generate sentences.  The resemblance between
ATN and the architecture is accidental, but it is interesting how two
different approaches share a similar division of responsibilities, while
having different quite semantics.

>>>>

\newacronym{PDA}{Pushdown Automata}{}
\newacronym{FA}{Finite Automata}{}
\newacronym{CFL}{Context-Free Languages}{}
\newacronym{SLCT}{Simple Logfile Clustering Tool}{}
\newacronym{SMTP}{Simple Mail Transfer Protocol}{}
\newacronym{ATN}{Augmented Transition Networks}{}

@@

There is some similarity (shown in \tableref{Similarities with ATN})
between the architecture and William Wood's 
\ATN{}~\cite{atns, nlpip}, a tool used in Computational Linguistics for
creating grammars to parse or generate sentences.  The resemblance between
\ATN{} and the architecture is accidental, but it is interesting how two
different approaches share a similar division of responsibilities, while
having different quite semantics.
